A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-05-29 sections/Related.tex
RW: the Essence of ML TypeInference

\paragraph{The Essence of ML Type-Inference} \bruno{we deal with
  higher-ranked polymorphism and do not have separate phases for 
constraint generation and solving. In such multi-phase algorithms 
there is typically a different constraint language. In contrast in our
single phase algorithm one could view the judgements as a form 
of constraints, and no separate constraint language is needed.
Other more technical differences?}

>>>>

\paragraph{The Essence of ML Type-Inference}
Constraint-based type inference is adopted by \citep{remy-attapl} for ML type systems,
which does not employ higher-ranked polymorphism.
Constraint generating and solving are typical phases for a constraint-based algorithm,
and an intermediate language is used to describe constaints.
Furthermore, their constraint solver utilizes a stack to track the state of
the solving process.
In contrast, our algorithm has a single phase,
where the judgment chains themselves act as constraints,
thus no separate constaint language is needed.
However, the constraint language provides a general and reuseable interface
that interprets the desired properties for type inference.

\bruno{we deal with higher-ranked polymorphism and do not have separate phases for 
constraint generation and solving. In such multi-phase algorithms 
there is typically a different constraint language. In contrast in our
single phase algorithm one could view the judgements as a form 
of constraints, and no separate constraint language is needed.
Other more technical differences?}
